% experiences.tex

\section{Experiences}

\cventry{Dec 2024--Present}{Backend Developer}{Carbon}{Tehran, Iran}{}{
    \begin{itemize}
        \item Managed and optimized \textbf{vSphere clusters, ESXi servers}, and \textbf{HA pfSense nodes} for reliable traffic management.
        \item Automated shared hosting deployments using \textbf{Bash} and \textbf{Ansible}, reducing setup time and improving efficiency.
        \item Implemented monitoring with \textbf{Prometheus}, \textbf{Grafana}, and \textbf{Zabbix} for proactive issue detection.
        \item Maintained \textbf{KVM clusters}, improving resource utilization and system performance.
        \item Designed and deployed \textbf{network infrastructure} and data center layouts, managing MikroTik and Cisco equipment for a redundant, high-availability network.
        \item Maintained \textbf{HPE server hardware and software}, ensuring stable and reliable operations.
    \end{itemize}
}

\cventry{Dec 2022--Feb 2024}{Backend Developer}{SmartMakran}{Tehran, Iran}{}{
    \begin{itemize}
        \item Managed and optimized \textbf{ESXi/vSphere servers}, including OS upgrades, resource tuning, and ongoing maintenance.
        \item Built and maintained CI/CD pipelines for developers, streamlining deployment workflows and improving delivery speed.
        \item Designed and implemented \textbf{backup strategies} for critical services, ensuring data reliability and rapid recovery.
        \item Containerized multiple services and maintained their infrastructure, improving scalability and operational consistency.
        \item Deployed and maintained \textbf{monitoring solutions} to ensure service reliability and proactive issue detection.
        \item Advised on \textbf{cloud architecture} and provided migration consulting to improve performance and reduce operational overhead.
    \end{itemize}
}
